Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-03 Scripts/Initial_Analysis.Rmd
re run model for speices that didnt work

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
       model = "GFDL",
      rcp = 85,
      path = "",
    )
  )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- my_path("R",extra_path = "Proportion")

@@

# EstPropChange(taxon_key = 600004,
#               year = year_df,
#               hist_y = 2000,
#               data_type = "Catch",
#               ensemble_list = ensemble_list,
#               path = path,
#               neighbours = neighbours)

@@

@@

####_______________________ ####
# Estimating proportion change
####_______________________ ####

t_start <- Sys.time()

mclapply(
  spp_list,
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensemble_list = ensemble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

>>>>

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
       model = "GFDL",
      rcp = "85",
      path = "NA",
      my_path = F
    )
  )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- paste(my_path("R",extra_path = "Proportion_n"),name,sep= "")

@@

# EstPropChange(taxon_key = 600004,
#               year = year_df$year,
#               hist_y = 2000,
#               data_type = "Catch",
#               ensemble_list = 102,
#               path = path,
#               neighbours = neighbours)
#

@@

modeled_spp <- list.files(my_path("R", extra_path = "Proportion_n"))

modeled_spp <- gsub("proportion_","",modeled_spp)
modeled_spp <- gsub(".csv","",modeled_spp)

spp_list <- spp_list[!spp_list %in% modeled_spp]

@@

####_______________________ ####
# Estimating proportion change
####_______________________ ####
gc()
t_start <- Sys.time()

mclapply(
  spp_list,
  EstPropChange,
  year <- year_df$year,
  data_type <- "Catch",
  ensemble_list = ensemble_list,
  path = DBEM_path,
  neighbours = Neighbours
)
